Sparse Function-space Representation \\ of Neural Networks

### 2023-05-19 paper/main.tex
Minor
update app. cl experiments

In our experiments, we compared the performance of \our-based regularizer against two families of methods: weight-space regularization methods and function-space regularization ones.
For the weight-space methods, we considered EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke2017continual}, and VCL~\citep{nguyen2018variational}.  % In \cref{tbl:cl_table_1}, we considered VCL with random coresets, which uses coreset points t 
For the function-space methods, we considered DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual}.

@@

>>>>

In our experiments, we compared the performance of \our-based regularizer against two families of methods: weight-space regularization methods and function-space regularization ones.
For the weight-space methods, we considered Online-EWC~\citep{schwarz2018progress}, SI~\citep{zenke2017continual}, and VCL~\citep{nguyen2018variational}.  % In \cref{tbl:cl_table_1}, we considered VCL with random coresets, which uses coreset points t 
For the function-space methods, we considered DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual}.

@@

%% Hyperparms used in the different experiments:
\textbf{S-MNIST (40 pts./task):}
\begin{itemize}
	\item[-] Online-EWC: SGD, learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
	\item[-] SI: SGD, learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
	\item[-] DER: SGD, learning rate 0.03, batch size 10, buffer batch size 10, number epochs 1, $\alpha=0.2$, reservoir buffer size 200.
	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$
	\item[-] S-FSVI: Adam, learning rate 
	\item[-] SFR: Adam
\end{itemize}

\textbf{S-MNIST (200 pts./task):}
\begin{itemize}
	\item[-] Online-EWC: SGD, learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
	\item[-] SI: SGD, learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
	\item[-] DER: SGD, learning rate 0.03, batch size 10, buffer batch size 10, number epochs 1, $\alpha$ 0.2, reservoir buffer size 1000.
	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$
	\item[-] S-FSVI: Adam
	\item[-] SFR: Adam
\end{itemize}

%% Placeholders for now
\textbf{S-FMNIST (200 pts./task):}
\begin{itemize}
	\item[-] Online-EWC: SGD, learning rate $0.03$, batch size  10, number of epochs 5, $\lambda=90$, $\gamma=1.0$.
	\item[-] SI: SGD, learning rate 0.1, batch size 10, number of epochs 5, $c=1.0$, $\xi=0.9$.
	\item[-] VCL (with coresets):
	\item[-] DER: SGD, learning rate 0.03, batch size 10, buffer batch size 10, number epochs 5, $\alpha$ 0.2, reservoir buffer size 200.
	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$
	\item[-] S-FSVI: Adam
	\item[-] SFR: Adam
\end{itemize}

\textbf{P-MNIST (200 pts./task):}
\begin{itemize}
	\item[-] Online-EWC: SGD
	\item[-] SI: SGD 
	\item[-] VCL (with coresets): Adam
	\item[-] DER: SGD
	\item[-] FROMP: Adam
	\item[-] S-FSVI: Adam
	\item[-] SFR: Adam
\end{itemize}
